---
title: "Misha Khan MSBA 277"
output: pdf_document
---
Install packages
```{r}
install.packages("psych") #Descriptive Statistics
install.packages("dplyr") #Data Manipulation
install.packages("plyr")
install.packages("tidyverse") #Essential R packages
install.packages("gtsummary") #Summary tables
install.packages("sqldf") #SQL
install.packages("ggplot2") #Data Visualization
install.packages("corrplot") #Correlation Plot
install.packages("igraph") #Graphs
install.packages("shiny") #Graphs
install.packages("car") #VIF
install.packages("MatchIt") #PSM

```

Load libraries
```{r}
library(psych)
library(dplyr)
library(plyr)
library(tidyverse)
library(gtsummary)
library(sqldf)
library(ggplot2)
library(corrplot)
library(igraph)
library(shiny)
library(car)
library(MatchIt)

```

Load file
```{r}
#Set working directory
#setwd("~/Desktop/WINTER 2020/MSBA 277/Midterm/HighNote Data Midterm.csv")

#Read file
data <- data.frame(read.csv("HighNote Data Midterm.csv", header = TRUE))
head(data)
attach(data)
sum(is.na(data))
```


1. Summary Statistics 
Generate descriptive statistics for the key variables in the data set, similar 
to the table on the last page of the case. (Note that your table will look 
different because the data set you are analyzing is different from the one used 
to generate the table in the case.) Analyze the differences in the mean values 
of the variables, comparing the adopter and non-adapter subsamples. 
What tentative conclusions can you draw from these comparisons? 
```{r}
stat <- data %>% select(age, male, friend_cnt, subscriber_friend_cnt, songsListened, playlists, posts, shouts, lovedTracks, friend_country_cnt, good_country, tenure, adopter)

stat %>% tbl_summary(by = adopter,
                     statistic = list(all_continuous() ~ "{mean} ({sd})",
                                      all_categorical() ~ "{n} / {N} ({p}%)"),
                     digits = all_continuous() ~4
                     ) %>% add_p()

```


2. Data Visualization
Generate a set of charts (e.g., scatter plots, box plots, etc) to help visualize
how adopters and non-adopters (of the premium subscription service) differ from
each other in terms of (i) demographics, (ii) peer influence, and (iii) user
engagement. What can you conclude from your charts? 
```{r}
#Create factor for adopter
adopter <- ifelse(data$adopter == 1, "Premium", "Free")
table(adopter)

```

```{r}
#(i) Demographics: age, male, good_country

##########################################
##################AGE#####################
##########################################
hist(data$age,
     breaks = 100,
     main = "Demographic: Distribution of Age",
     xlab = "Range",
     col = "light blue")

ggplot(data, aes( x = age, group = adopter, fill = adopter)) +
  #geom_density(alpha = 0.3) +
  geom_histogram(position = "identity", binwidth = 0.5) + theme()

##########################################
#################MALE#####################
##########################################
ggplot(data, aes(x = male, group = adopter, fill = adopter)) +
  #geom_count(aes(x = male, y = adopter)) +
  geom_bar(position = "dodge") +theme()


##########################################
################COUNTRY###################
##########################################
ggplot(data, aes(x = good_country, group = adopter, fill = adopter)) +
  geom_bar(position = "dodge") + theme()

##########################################
##############CORRELATION#################
##########################################
demo_corr <- data[, c('adopter', 'age', 'male', 'good_country')]
x = cor(demo_corr, method = c("pearson", "kendall", "spearman"))
corrplot(x, method = "number", addrect = 2)
   
```


```{r}
#(ii) Peer Influence: friend_cnt, avg_friend_age, avg_friend_male, friend_country_cnt, subscriber_friend_cnt

##########################################
###############FRIEND COUNT###############
##########################################
friend.count <- ggplot(data, aes(x = adopter, y = friend_cnt, fill = adopter)) +
  geom_bar(stat = "summary") 

friend.count

##########################################
###############FRIEND AGE#################
##########################################
friend.age <- ggplot(data, aes(x = adopter, y = avg_friend_age, fill = adopter)) +
  geom_bar(stat = "summary") 

friend.age

##########################################
###############FRIEND MALE################
##########################################
friend.male <- ggplot(data, aes(x = adopter, y = avg_friend_male, fill = adopter)) +
  geom_bar(stat = "summary") 

friend.male

##########################################
###############FRIEND COUNTRY#############
##########################################

friend.country <- ggplot(data, aes(x = adopter, y = friend_country_cnt, fill = adopter)) +
  geom_bar(stat = "summary") 

friend.country

##########################################
###############FRIEND SUB#################
##########################################
friend.sub <- ggplot(data, aes(x = adopter, y = subscriber_friend_cnt, fill = adopter)) +
  geom_bar(stat = "summary") 

friend.sub

##########################################
##############CORRELATION#################
##########################################
peer_corr <- data[, c('adopter', 'friend_cnt', 'avg_friend_age', 'avg_friend_male', 'friend_country_cnt', 'subscriber_friend_cnt')]
x = cor(peer_corr, method = c("pearson", "kendall", "spearman"))
corrplot(x, method = "number", addrect = 2)

```

```{r}
#(iii) User Engagement: songsListened, lovedTracks, posts, shouts, playlists, tenure

##########################################
###############SONGS LISTENED#############
##########################################
SL <- ggplot(data, aes(x = adopter, y = songsListened, fill = adopter)) +
  geom_bar(stat = "summary") 

SL

##########################################
###############LOVED TRACKS###############
##########################################
LT <- ggplot(data, aes(x = adopter, y = lovedTracks, fill = adopter)) +
  geom_bar(stat = "summary") 

LT

##########################################
################# POSTS ##################
##########################################
PST <- ggplot(data, aes(x = adopter, y = posts, fill = adopter)) +
  geom_bar(stat = "summary") 

PST

##########################################
###############PLAYLISTS#################
##########################################
PLAY <- ggplot(data, aes(x = adopter, y = playlists, fill = adopter)) +
  geom_bar(stat = "summary") 

PLAY

##########################################
###############SHOUTS####################
##########################################
SHT <- ggplot(data, aes(x = adopter, y = shouts, fill = adopter)) +
  geom_bar(stat = "summary") 

SHT

##########################################
###############TENURE####################
##########################################
TEN <- ggplot(data, aes(x = adopter, y = tenure, fill = adopter)) +
  geom_bar(stat = "summary") 

TEN

##########################################
##############CORRELATION#################
##########################################
eng_corr <- data[, c('adopter', 'songsListened', 'lovedTracks', 'posts', 'playlists', 'shouts', 'tenure')]
x = cor(eng_corr, method = c("pearson", "kendall", "spearman"))
corrplot(x, method = "number", addrect = 2)

```

3. Propensity Score Matching 
You will use PSM to test whether having subscriber friends affects the 
likelihood of becoming an adopter (i.e., fee customer). For this purpose, the
"treatment" group will be users that have one or more subscriber friends
(subscriber_friend_cnt >= 1), while the "control" group will include users with
zero subscriber friends. Use PSM to first create matched treatment and control
samples, then test whether there is a significant average treatment effect.
Provide an interpretation of your results.
```{r}
# Pre-analysis using non-matched data
#Difference in means: pretreatment covariate

#Create binary variable for subscriber_friend_cnt
data$subscriber_friend_cnt <- ifelse(data$subscriber_friend_cnt >= 1, 1, 0)
data_cov <- c('age','male','friend_cnt','avg_friend_age','avg_friend_male','friend_country_cnt','songsListened','lovedTracks','posts','playlists','shouts','tenure','good_country')

data %>%
  group_by(subscriber_friend_cnt) %>%
  select(one_of(data_cov)) %>%
  summarise_all(funs(mean(., na.rm = T)))

with(data, t.test(subscriber_friend_cnt ~ adopter))
#P < alpha, data is not similar among groups
```

```{r}
#Propensity Score estimation (without log, unmatched data)
data_psm <- glm(subscriber_friend_cnt ~ age + male + friend_cnt + avg_friend_age + avg_friend_male + friend_country_cnt + songsListened + lovedTracks + posts + playlists + shouts + tenure + good_country, family = binomial(), data = data)

summary(data_psm)
```

```{r}
#In order to take log, find the variables with minimum of 0 to add plus 1 (avoid taking log of 0)
min(age) #8
min(friend_cnt) #1
min(avg_friend_age) #8
min(avg_friend_male) #0 ***
min(friend_country_cnt) #0 ***
min(songsListened) #0 ***
min(lovedTracks) #0 ***
min(posts) #0 ***
min(playlists) #0 ***
min(shouts) #0 ***
min(tenure) #0 ***
min(good_country) #0 ***

#We don't add 1 to age, friend_cnt, and avg_friend_age.
```

```{r}
#Propensity Score estimation (with log, unmatched data)
logit <- glm(subscriber_friend_cnt ~ log(age) + male +log(friend_cnt) + log(avg_friend_age) + log(avg_friend_male + 1) +
                        log(friend_country_cnt + 1) + log(songsListened + 1) + log(lovedTracks + 1) + log(posts + 1) +
                        log(playlists + 1) + log(shouts + 1) + log(tenure + 1) + good_country,
                        family = binomial(),
                        data = data)
summary(logit)
```

```{r}
# Using this model, we can now calculate the propensity score for each user 
# It is simply the user’s predicted probability of being Treated, 
# given the estimates from the logit model.
psm_df <- data.frame(pr_score = predict(logit, type = "response"),
                     treatment = logit$model$subscriber_friend_cnt)
head(psm_df)
```

```{r}
#Examining region of common support (logit)
#After estimating the propensity score, it is useful to plot histograms of the estimated propensity scores by treatment status

region <- paste("User Type:", c("Premium", "Free"))
psm_df %>%
  mutate(treatment = ifelse(treatment == 1, region[1], region[2])) %>%
  ggplot(aes(x = pr_score)) +
  geom_histogram(color = "black", fill = "pink") +
  facet_wrap(~treatment) +
  xlab("Probability of One or More Subscriber Friends") +
  theme_classic()

#Check NA values
sum(is.na(data))
```


```{r}
# The method we use below is to find pairs of observations that have very similar propensity scores, 
# but that differ in their treatment status. We use the package MatchIt for this. 
# This package estimates the propensity score in the background and then matches observations based 
# on the method of choice (“nearest” in this case).
data_match <- matchit(subscriber_friend_cnt ~ age + male + friend_cnt + avg_friend_age + avg_friend_male + friend_country_cnt + songsListened +lovedTracks + posts + playlists + shouts + tenure + good_country, method = "nearest", data = data)

# We can get some information about how successful the matching was using summary(mod_match) and plot(mod_match)
#Matching information
summary(data_match)
plot(data_match)

# To create a dataframe containing only the matched observations, use the match.data() function
#Use matching observations
data_m <- match.data(data_match)
dim(data_m)
table(data_m$subscriber_friend_cnt)
```


```{r}
#Log of Matching data
log_match <- matchit(subscriber_friend_cnt ~ log(age) + male + log(friend_cnt) + log(avg_friend_age) + log(avg_friend_male + 1) + log(friend_country_cnt +1) +
                                  log(songsListened + 1) + log(lovedTracks + 1) + log(posts + 1) + log(playlists + 1) + log(shouts + 1) + log(tenure + 1) +
                                  good_country, 
                                  method = 'nearest',
                                  data = data,
                                  caliper = 0.1)
summary(log_match, covariates = T)

#Match the new log data
log_m <- match.data(log_match)
dim(log_m)
table(log_m$subscriber_friend_cnt)

lapply(data_cov, function(v) {
  t.test(log_m[, v] ~ log_m$subscriber_friend_cnt)
})

```

```{r}
# Difference in means (matched data)
group_by(data_m, subscriber_friend_cnt) %>%
  summarise_all(funs(mean(., na.rm = T)))
lapply(data_cov, function(v) {
  t.test(data_m[,v] ~ data_m$subscriber_friend_cnt)
})
```


```{r}
# Estimating treatment effects
#Treatment #1: All unmatched
lm_1 <- glm(adopter ~ subscriber_friend_cnt, data = data_m, family = binomial(), )

summary(lm_1)
with(data_m, t.test(adopter ~ subscriber_friend_cnt))

#p < alpha reject null
#more than 0 or 1 subscriber friend youre more likely to be an adopter

#Treatment #2: Covariate (both significant and insignificant)
lm_2 <- glm(adopter ~ subscriber_friend_cnt +log(age) + male + log(friend_cnt) + log(avg_friend_age) + log(avg_friend_male + 1) + log(friend_country_cnt +1) +
                                  log(songsListened + 1) + log(lovedTracks + 1) + log(posts + 1) + log(playlists + 1) + log(shouts + 1) + log(tenure + 1) +
                                  good_country, data = data_m, family = binomial())
summary(lm_2)

#avgmale friends and foreign friends doesn't affect if you are adopter or not

```
 
4. Regression Analysis
Now, we will use a logistic regression approach to test which variables
(including subscriber friends) are significant for explaining the likelihood of
becoming an adopter. Use your judgment and visualization results to decide which
variables to include in the regression. Estimate the odds ratios for the key
variables. What can you conclude from your results?
```{r}
#Full model of full data
full.mod <- lm(adopter ~ log(age) + male + log(friend_cnt) + log(avg_friend_age) + log(avg_friend_male + 1) + log(friend_country_cnt +1) +
                                  log(songsListened + 1) + log(lovedTracks + 1) + log(posts + 1) + log(playlists + 1) + log(shouts + 1) + log(tenure + 1) +
                                  good_country + subscriber_friend_cnt,
                                  data = data,
                                  family = binomial())
summary(full.mod)

```
After running regression on the model, we can see that the log(friend_cnt) and log(avg_friend_male +1) are insignifican based on alpha = 0.05.
Rest are not significant so we keep this in our model.
```{r}
#Reduced model of full data
#Remove log(friend_cnt) and log(avg_friend_male +1)
reduced.mod <- lm(adopter ~ log(age) + male + log(avg_friend_age) + log(friend_country_cnt +1) +
                                  log(songsListened + 1) + log(lovedTracks + 1) + log(posts + 1) + log(playlists + 1) + log(shouts + 1) + log(tenure + 1) +
                                  good_country + subscriber_friend_cnt,
                                  data = data,
                                  family = binomial())
summary(reduced.mod)
```
```{r}
#Now we run anova with both full and reduced to compare (full data)
anova(full.mod, reduced.mod, test = "Chisq")
```
Chisq = 0.1747
Chisq p value is insignificant
suggests that the reduced model fits as well as the full model for the full dataset
```{r}
#Full model on matched data
full.mod.m <- lm(adopter ~ log(age) + male + log(friend_cnt) + log(avg_friend_age) + log(avg_friend_male + 1) + log(friend_country_cnt +1) +
                                  log(songsListened + 1) + log(lovedTracks + 1) + log(posts + 1) + log(playlists + 1) + log(shouts + 1) + log(tenure + 1) +
                                  good_country + subscriber_friend_cnt,
                                  data = data_m,
                                  family = binomial())
summary(full.mod.m)
```
After running regression on the model with matched data, we can see that the log(avg_friend_male +1) and log(friend_country_cnt +1) are insignificant based on alpha = 0.05 (p>a).
Rest are not significant so we keep this in our model.
```{r}
reduced.mod.m <- lm(adopter ~ log(age) + male + log(friend_cnt) + log(avg_friend_age) +
                                  log(songsListened + 1) + log(lovedTracks + 1) + log(posts + 1) + log(playlists + 1) + log(shouts + 1) + log(tenure + 1) +
                                  good_country + subscriber_friend_cnt,
                                  data = data_m,
                                  family = binomial())
summary(reduced.mod.m)
```
```{r}
#Now we run anova with both full and reduced to compare (matched)
anova(full.mod.m, reduced.mod.m, test = "Chisq")
```
Chisq = 0.49 therefore insignificant
Reduced model fits as well as the full model

```{r}
#Estimate odds ratio for the key variables.
exp(reduced.mod$coefficients) - 1
exp(reduced.mod.m$coefficients) -1

```

